\documentclass{article}
\usepackage[utf8]{inputenc}
\include{loc}
%\usepackage{soul}
\usepackage{geometry}
\newgeometry{vmargin={30mm}, hmargin={30mm}}

\begin{document}
\hspace*{\fill} Lazarev Cleaver LLP\\
\hspace*{\fill}Warnford Court\\
\hspace*{\fill}29 Throgmorton Street\\
\hspace*{\fill}London EC2N 1AT\\
\hspace*{\fill}Telephone: +44 20 7987 6300\\
\hspace*{\fill}Email: reception@lcllp.co.uk\par

\noindent\firstperson\\
\secondperson\\
\street\\
\locality\\
\town\\
\postcode\par
\vspace{5 mm}
\noindent\dateset\par
\vspace{3 mm}
\noindent\textbf{\sendmethod}\par
\vspace{3 mm}
\noindent Dear \borrower\par
\vspace{3 mm}
\noindent\textbf{Re: \property\ (the "Premises")\pone (Title number \tnumber (the “Lease”)}
\vspace{3 mm}
\par
\noindent We act on behalf of \propowner\ and its agent, Urang Property Management Ltd, in relation to the \charges\ arrears due in respect of the above Premises. Pursuant to \clause\ of the Lease you are
liable to pay \charges\ to our client.
\vspace{3 mm}
\par
\noindent\underline{Arrears}\\
Our client sent you \charges\ demands and reminders on a number of occasions, including on \demanddate. Despite our client’s demands and reminders, and in breach of the terms of your Lease, you have failed to pay the \charges\ At the date of this letter the total amount outstanding in respect of the \charges\ is \total\ as set out in the enclosed statement of account.
\vspace{3 mm}
\par
\interest
\newpage
\costs
\noindent\underline{Claim}\\
We are instructed to commence legal proceedings against you unless you pay the full amount of outstanding charges and legal costs within 14 days of the date of this letter. Accordingly, we request that you pay the amount of £8,825.90 by 4 pm on 18 November 2020. Payment may be made by cheque or banker’s draft made payable to “Lazarev Cleaver LLP” and sent to the address at the top of this letter. Alternatively, payment may be made by electronic bank transfer to the following account:
\vspace{3 mm}
\par
\indent Name: Lazarev Cleaver LLP Client Account\\
\indent Sorting code: 40-18-22\\
\indent Account number: 23668029\\
\indent Reference: GL/198.00124
\vspace{3 mm}
\par
\noindent All payments should be made to this firm. Our client will refuse to accept any payment unless
legal costs are included, or will apply funds to the legal costs first so that you will continue to
remain liable for any shortfall. We will also charge a fee of £100 plus VAT to cover the cost of
our correspondence with our client and you.

\vspace{3 mm}
\par
\noindent\underline{Forfeiture}\\
Should you fail to pay the outstanding charges, our instructions are to pursue this matter and
\forfeitureOne\ to seek forfeiture of your Lease under the terms of \forfeitureTwo\ of the
Lease. 

\vspace{3 mm}
\par

\noindent\textit{\underline{Pre-action matters and financial advice}}\\
We draw your attention to the Civil Procedure Rules and the Practice Direction—Pre-Action
Conduct and Protocols, including paragraphs 13 to 16 regarding the consequences of failure
to comply with its provisions. A copy of the Protocol is available at the following web address:\\
https://www.justice.gov.uk/courts/procedure-rules/civil/rules/pd\_pre-action\_conduct.\\\vspace{1 mm}

\noindent We have also set out below details of independent advice organisations who provide free
independent advice and assistance should you require their services.\\\vspace{1 mm}

\noindent Should you wish to discuss the contents of this letter, you may contact us by email at
reception@lcllp.co.uk or by calling 020 7987 6300, quoting reference \caseno.\\\vspace{3 mm}
Yours sincerely\\\vspace{3 mm}
Lazarev Cleaver LLP\\\vspace{3 mm}
Encl

\end{document}
